Efficient pedigree recording for fast population genetics simulation

### 2018-01-03 forwards_paper.tex
add GC interval text to paper

\jda{Maybe we should quantify the factor by which RAM use increased; it's not
	easy to read off the figures}
Our method uses more RAM (up to 2 orders of magnitude more) than simple forward simulations (see~\ref{ss:memuse_nosel}),
although in practice shorter simplification intervals may reduce RAM use
(but at a slight cost to the speed up achieved, see~\ref{ss:seq_simp}).
The benefits to our method are not limited to situations with selection:
in a more limited set of neutral simulations we found the same qualitative
behavior with a numerically larger benefit to pedigree tracking (see~\ref{ss:speedup_nosel}).

@@

\section{Timing with no selection}
\label{ss:timing_nosel}
\renewcommand{\thefigure}{C\arabic{figure}}
\setcounter{figure}{0}

>>>>

\jda{Maybe we should quantify the factor by which RAM use increased; it's not
	easy to read off the figures}
Our method uses more RAM (up to 2 orders of magnitude more) than simple forward simulations (see~\ref{ss:memuse}),
although in practice shorter simplification intervals may reduce RAM use
(but at a slight cost to the speed up achieved, see~\ref{ss:gcinterval}).
The benefits to our method are not limited to situations with selection:
in a more limited set of neutral simulations we found the same qualitative
behavior with a numerically larger benefit to pedigree tracking (see~\ref{ss:timing_nosel}).

@@

\newpage

\section{Effect of simplification interval on run time and memory use}
\label{ss:gcinterval}

We performed a limited set of simulations to explore the effect of the simplification interval on run times and memory
use. Figure~\ref{sfig:gctime} shows that run times increase for simplification intervals less than 100 generations.  For
intervals $\geq 100$ generations, run times are very similar, with no appreciable difference between $10^3$ and $10^4$
generations.  As expected, the simplification interval has a near-linear effect on peak RAM use
(Figure~\ref{sfig:gcmem}).  Taken together Figures~\ref{sfig:gctime} and~\ref{sfig:gcmem} suggest that one can tune the
simplification interval to available RAM with little effect on run times provided that simplification doesn't occur too
often.

\begin{figure}[!h]
    \includegraphics{sims/gc_interval/GCtime}
    \caption{\label{sfig:gctime}The effect of simplification interval on run times.  A single replicate was done for the
        parameters shown in the figure.  These simulations were done with the same selection parameters as in
    Figure~\ref{fig:runtimes_selection}.}
\end{figure}

\begin{figure}[!h]
    \includegraphics{sims/gc_interval/GCmem}
    \caption{\label{sfig:gcmem}Peak RAM use for the simulations shown in Figure~\ref{sfig:gctime}.}
\end{figure}

\newpage
\section{Timing and memory use with no selection}
\label{ss:timing_nosel}
\renewcommand{\thefigure}{C\arabic{figure}}
\setcounter{figure}{0}
